---
format: gfm
---

<!-- README.md is generated from README.qmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# libipldr

<!-- badges: start -->
[![R-CMD-check](https://github.com/JBGruber/libipldr/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/JBGruber/libipldr/actions/workflows/R-CMD-check.yaml)
[![extendr](https://img.shields.io/badge/extendr-^0.8.1-276DC2)](https://extendr.github.io/extendr/extendr_api/)
<!-- badges: end -->

The goal of libipldr is to make it possible to translate DAG-CBOR encoded data in R.
This is mostly useful for the [`atrrr`](https://jbgruber.github.io/atrrr/articles/Networks.html) package that can stream from the Bluesky firehose.

## Installation

You can install the development version of libipldr with:

``` r
install.packages("libipldr)
```

Or install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("JBGruber/libipldr")
```

## Example

Decode CID:

```{r}
library(libipldr)
decode_cid("bafyreig7jbijxpn4lfhvnvyuwf5u5jyhd7begxwyiqe7ingwxycjdqjjoa")
```

Decode DAG-CBOR:

```{r}
cbor_data <- as.raw(c(
  0xa2, 0x61, 0x61, 0x65, 0x48, 0x65, 0x6c, 0x6c, 0x6f, 0x61, 0x62,  0x66, 0x57, 0x6f, 0x72, 0x6c, 0x64, 0x21
))
decode_dag_cbor(cbor_data)
```

# What is this good for?

Mainly I wanted to have this to decode the firehose stream from Bluesky:

```{r}
library(httr2)
# open connection to firehose
firehose <- request("wss://bsky.network/xrpc/com.atproto.sync.subscribeRepos") |>
  req_perform_connection()

# stream 5 Mb
results_raw <- firehose |>
  resp_stream_raw(kb = 5000)

close(firehose)

# decode the stream
results <- decode_dag_cbor_multi(results_raw)

# extract operations
library(purrr)
library(dplyr)
events_df <- map(results, function(res) {
  pluck(res, "ops", 1)
}) |>
  bind_rows()
events_df
```

